Testing SEACells results

### 2024-11-08 analyses/metacells/notebooks/testing-seacells.Rmd
try not specifying conda environment for reticulate

```{r setup}
library(ggplot2)
library(reticulate)
reticulate::use_condaenv("openscpca-metacells")
```

@@

# these files were created by the `scripts/run-seacells.py` script
sc_anndata_file <- file.path(results_dir, paste0(params$library_id, "_seacells.h5ad"))
sc_model_file <- file.path(results_dir, paste0(params$library_id, "_seacells_model.pkl"))

```

@@

```{r purity_plot}
ggplot(py$purity, aes(y = singler_celltype_ontology_purity)) +
  geom_boxplot() +
  labs(title = "Celltype purity",
       y = "Celltype purity (singler)")
```

>>>>

```{r setup}
library(ggplot2)
library(reticulate)
# reticulate::use_condaenv("openscpca-metacells")
```

@@

# these files were created by the `scripts/run-seacells.py` script
sc_anndata_file <- file.path(results_dir, paste0(params$library_id, "_seacells.h5ad"))
sc_model_file <- file.path(results_dir, paste0(params$library_id, "_seacells_model.pkl"))
```

@@

```{r purity_plot}
ggplot(py$purity, aes(y = singler_celltype_ontology_purity)) +
  geom_boxplot() +
  labs(
    title = "Celltype purity",
    y = "Celltype purity (singler)"
  )
```
